---
title: "Eating Out"
author: "Miguel Avila"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "Fall 2024"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## There were two years in which the General Social Survey asked about the frequency of eating out. The variable name you are looking for is "eatout".
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=FALSE}
GSS <-read.dta(file="GSSxxxx.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(haven)
require(knitr)
require(foreign)
library(plyr)
```
```{r, eval=TRUE, warning=FALSE}
GSS <-read_dta(file="GSS1998.dta")
#GSS <- readstata13::read.dta13(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)

```

# Methods

Race is Cat
Eating out is Cat
Thus we use the Cat~Cat helper file

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```
Races are white,black, other. Blue represent ate out last week. Orange represents didn't eat out last week.      
The bar chart shows that white people eat out the most and eat in the least.Black people eat out the least and eat in the most.     

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```
The numerical shows that 83.11% white people eat out at least once a week and 16.89% don't.   


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisherXY(mydata$race,mydata$eatout,printAll = T)
```

The chi square test shows that the p-value is 0.000002287, so we reject $H_0$. So, there is a statistical difference between at least two races with the frequency of eating out.   

The Fisher test has a p-value of of 0.00001183 so there is a statistical difference between white and black people in the frequency of eating out.

The